Btech Project - Progress Diary

### 2017-07-26 Work_report/Daily_progress/work_progress_daily.tex
Adding a few papers
Adding paper review #1

\bibliography{./papers.bib}
\bibliographystyle{ieeetr}
% \nocite{*}

>>>>

\subsubsection{July 21 : Friday}
No work done.

\subsubsection{July 22 : Saturday}
No work done

\subsubsection{July 23 : Sunday}
No work done.

\subsubsection{July 24 : Monday}
Meeting with Sayan. Discussion about some basic problems that could be solved. Apparently Video Co-segmentation using Deep learning is not yet looked upon. May be a good breakthrough.

\subsubsection{July 25 : Tuesday}
Target :
\begin{itemize}
\item Read the three papers. \cite{7120111} , \cite{7401081}, \cite{Zhang2014}
\end{itemize}

Accomplished :
\begin{itemize}
\item Able to read only 1 paper properly (not too properly).
\end{itemize}

\subsubsection{July 26 : Wednesday}

\begin{itemize}
\item Couldn't do much. Need to do paper review at the very first.
\item Need to do pytorch tutorials as well.
\item Paper review to be done in a separate file.
\end{itemize}

\bibliography{./papers.bib}
\bibliographystyle{ieeetr}

%\nocite{*}
